Classless Java

### 2015-11-16 paper/sections/Translation.tex
First draft of translation and proof.

\noindent\textbf{LEMMA. }
If $\II_0$ OK, then $[\![\II_0]\!]$ OK.
\begin{proof}
First assume that $\II_0$ is of form $$\mixinAnn\ \QM{interface}\ C_0\ \QM{extends}\ \overline{C}\ \oC \methods\ \cC$$
By the rule \rn{t-Invk} in Figure~\ref{ET}, we divide it into two parts.

@@

\noindent\textbf{Part II.} Next we check $\dom(C_0)=\dom(C_1)\cup\ldots\cup\dom(C_n)\cup\dom(\methods)\cup\dom(\methods')$.

@@

>>>>

\noindent\textbf{LEMMA 1. }
If $\II_0$ satisfies $\dom(C_0)=\dom(C_1)\cup\ldots\cup\dom(C_n)\cup\dom(\methods)$, then $[\![\II_0]\!]$ satisfies $\dom'(C_0)=\dom(C_1)\cup\ldots\cup\dom(C_n)\cup\dom(\methods)\cup\dom(\methods')$.
\begin{proof}
It suffices to prove $\dom'(C_0)=\dom(C_0)\cup\dom(\methods')$.
\begin{itemize}
\item If $m\notin\dom(\methods')$, by the definition of $\mBody$, it is obtained from $\override$. The first argument of $\override$, namely $\methods\cup\methods'(m)$, is equal to $\methods(m)$, and the second argument is not changed as well, thus the result of $\override$ is not changed during translation. Hence $m\in\dom'(C_0)$ iff $m\in\dom(C_0)$.
\item If $m\in\dom(\methods')$, we are to prove $m\in\dom'(C_0)$. So if $m$ is the $\QM{of}$ method generated by $\ofMethod$, its $\mBody$ value is well defined, by the rule $\override(\method,\none)=\method$. On the other hand, if $m$ is generated by $\otherMethod$, namely $m$ is a $\QM{with-}$ or setter method, we can also get its $\mBody$ value, since in the definition of $\otherMethod$, we can see $\isWith$ and $\isSetter$ ensure the compatible subtyping relationship. Hence $m\in\dom'(C_0)$ as well.
\end{itemize}
\end{proof}

\noindent\textbf{LEMMA 2. }
If $\II_0$ OK, then $[\![\II_0]\!]$ OK.
\begin{proof}
First assume that $\II_0$ is of form $$\mixinAnn\ \QM{interface}\ C_0\ \QM{extends}\ \overline{C}\ \oC \methods\ \cC$$
By the rule \rn{t-Invk} in Figure~\ref{ET}, we divide it into two parts.

@@

\noindent\textbf{Part II.} Next we check that in $[\![\II_0]\!]$, $$\dom(C_0)=\dom(C_1)\cup\ldots\cup\dom(C_n)\cup\dom(\methods)\cup\dom(\methods')$$
And actually it is guaranteed by \textbf{LEMMA 1}.

@@

\begin{proof}
\textbf{(THEOREM) LEMMA 2} already proves that $[\![\II_0]\!]$ is OK. On the other hand, if some $\II$ is not a subtype of $\II_0$, the generated code in translation has no way to affect the domain of $\II$, which finishes our proof.
\end{proof}
